Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-05-17 xrb3/paper.tex
update

Our simulations complement the two- and three-dimensional models of flames of
\citet{cavecchi:2013,art-2015-cavecchi-etal,art-2016-cavecchi-etal,Cavecchi2019}
by focusing on resolving the reaction zone of the flame and modeling
the vertical structure hydrodynamically instead of hydrostatically.
We also focus on modeling flames starting from a small hot spot.  This
however means that we are confined to smaller domains, with similar
computational resources, so one of the goals of this study is to
understand how far we can push resolved XRB flame simulations.  The
work by \citet{goodwin:2021} also explores multidimensional evolution,
looking at the thermal transport and how affects the location where
the hotspot ignites.  Together, all three approaches help build a
comprehensive multidimensional picture of X-ray bursts.

@@

\begin{figure}[t]
\centering
\plotone{mass_plot}
\caption{\label{fig:mass_plot} Mass of species scaled to initial He
  mass as a function of time.  The 3D simulation is shown as the solid
  lines and the 2D simulation is shown as the dashed lines.}
\end{figure}

@@

These results also suggest that we can do initial explorations of full
star bursts in two-dimensions, perhaps using axisymmetric spherical
coordinates (modeling an annular region in $r$-$\theta$).  In this
geometry, point ignition requires starting at the poles, but this
would allow us to see the effect of varying gravity with latitude (due
to centrifugal forces), as well as begin to consider lightcurve modeling.

>>>>

Our simulations complement the two- and three-dimensional models of flames of
\citet{cavecchi:2013,art-2015-cavecchi-etal,art-2016-cavecchi-etal,Cavecchi2019}
by focusing on resolving the reaction zone of the flame and modeling
the vertical structure hydrodynamically instead of hydrostatically.
We also focus on modeling flames starting from a small hot spot.  This
however means that we are confined to smaller domains, with similar
computational resources, so one of the goals of this study is to
understand how far we can push resolved XRB flame simulations.  The
work by \citet{goodwin:2021} also explores multidimensional evolution,
looking at the thermal transport and how \edit1{it} affects the location where
the hotspot ignites.  Together, all three approaches help build a
comprehensive multidimensional picture of X-ray bursts.

@@

\begin{figure}[t]
\centering
\plotone{mass_plot}
\caption{\label{fig:mass_plot} Mass of species scaled to \edit1{total}
  mass as a function of time.  The 3D simulation is shown as the solid
  lines and the 2D simulation is shown as the dashed lines.}
\end{figure}

@@

These results also suggest that we can do initial explorations of full
star bursts in two-dimensions, perhaps using axisymmetric spherical
coordinates (modeling an annular region in \edit1{neutron star radius and colatitude}).  In this
geometry, point ignition requires starting at the poles, but this
would allow us to see the effect of varying gravity with latitude (due
to centrifugal forces), as well as begin to consider lightcurve modeling.
